Expanding tidy data principles to facilitate missing data exploration, visualization and assessment of imputations

### 2018-09-06 paper/tidy-missing-data-paper.Rmd
add installation instructions

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      fig.align = "center",
                      # dev = c("png"), 
                      # dpi = 300,
                      fig.width = 4, 
                      fig.height = 4, 
                      cache = TRUE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
library(ggthemes)
library(png)
library(scales)
library(simputation)
library(naniar)
library(knitr)
library(lubridate)
library(magick)

>>>>

```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE, 
                      warning = FALSE, 
                      fig.align = "center",
                      fig.width = 4, 
                      fig.height = 4, 
                      cache = TRUE)
library(tidyverse)
library(gridExtra)
library(kableExtra)
library(ggthemes)
library(png)
library(scales)
library(simputation)
# if paper doesn't compile, use development version of naniar
# install.packages("remotes")
# remotes::install_github("njtierney/naniar")
library(naniar) 
library(knitr)
library(lubridate)
library(magick)
